---
title: "Welcome_to_University"
output: html_document
version: "duygu2051"
---
#Exploring OSYM 2017 Data

Here are the libraries that we are going to use:
```{r}
library(data.table)
library(dplyr)
library(ggplot2) # visualization
library(scales) # visualization
library(dplyr) # data manipulation
Sys.setlocale(locale = "Turkish_Turkey.1254")

```
We control our workspace path and after confirmation we load OSYM 2017 data as follows:
```{r}
getwd()
#load("C:/Users/merye/Desktop/osym_data_2017.RData")
download.file("https://mef-bda503.github.io/files/osym_data_2017_v2.RData", 
    "osym_data_2017.Rdata")
load("osym_data_2017.RData")
```

Dimensions for reshaped data are:
```{r}
d=osym_data_2017 %>% mutate(general_quota =as.numeric(general_quota),general_placement=as.numeric(general_placement))

dim(d)
```

We give an alias to our dataset as 'd' and see the detailed information about data:
```{r}
glimpse(d)
```
Let's see average values of minimum and maximum scores of the universities:
```{r}
d %>% group_by(university_name) %>% summarise(avgmin=mean(min_score),avgmax=mean(max_score))
```
We excluded abroad universities and state universities by using *filter* and give it a new name:
```{r}
dtr=d %>% filter(!(substr(program_id,1,1) %in% c('3','4','1')))
print(dtr)
```
```{r}
dim(d)
```
Later we groupped private universities in Ä°stanbul by their program names and ordered by max scores in descending order to compare their success orders.
```{r}
dtr %>% filter(city=='ÝSTANBUL') %>% select(university_name,program_name,max_score,general_quota,general_placement)  %>% group_by(program_name) %>%  arrange(desc(max_score))
```

To get a better look on the data, we calculated quota fill rate of these universities and ordered them by teir fill rates

```{r}
dpr = dtr %>% filter(city=='ÝSTANBUL') %>% group_by(university_name) %>% summarise(sayi =n(), totalquota=sum(as.numeric(general_quota)), totalplacement=sum(general_placement), fillrate =sum(totalplacement*100/totalquota))  %>% group_by(university_name) %>%  arrange(desc(fillrate))

print(head(dpr,100))
```
We find that MEF University has a fill rate of over 90 percent:
```{r}
dpr %>%  filter(university_name=="MEF ÜNÝVERSÝTESÝ")

```
Let's visualize our private universities data with bar a chart

```{r}
#dord=order(dpr$fillrate)
#dord2=head(dord,12)
dpr$university_name=substr(dpr$university_name,1,10)
dpr=head(dpr,12)
ggplot(data=dpr, aes(x=reorder(dpr$university_name, desc(dpr$fillrate)),y=dpr$fillrate,fill=dpr$fillrate))+
theme(axis.text.x = element_text(angle = 60, hjust=1))+
geom_bar(stat="identity",width = 0.95)+
   labs(title = "Top 12 Private Universities in Ýstanbul By Quota Fill Rate")+
    labs(x = "Universities", y = "Quota\nFill Rate") +
expand_limits(y=100)
```

