---
title: "Welcome_to_University"
output: html_document
---


Here are the libraries that we are going to use:
```{r}
library(data.table)
library(dplyr)
options(dplyr.width=Inf)
library('ggplot2') # visualization
library('scales') # visualization
library('dplyr') # data manipulation
Sys.setlocale(locale = "Turkish_Turkey.1254")

```
We load OSYM 2017 data as follows:
```{r}
getwd()
load("C:/Users/merye/Desktop/osym_data_2017.RData")
d=osym_data_2017
```

Dimensions of our data are `r dim(osym_data_2017)`.


```{r}
glimpse(d)
```

We excluded abroad universities and state universities by using *filter*:
```{r}
dtr=d %>% filter(!(substr(program_id,1,1) %in% c('3','4','1')))
print(dtr)
```

Later we groupped private universities in Ýstanbul by their program names and ordered by max scores in descending order.
```{r}
dtr %>% filter(city=='ÝSTANBUL') %>% select(university_name,program_name,max_score,general_quota,general_placement)  %>% group_by(program_name) %>%  arrange(desc(max_score))
```

Private universities in Ýstanbul grouped by their names. Their total general quota 

```{r}
dpr = dtr %>% filter(city=='ÝSTANBUL') %>% group_by(university_name) %>% summarise(sayi =n(), toplamkota=sum(general_quota), toplamyerlesen=sum(general_placement), doluluk_yuzdesi =sum(toplamyerlesen*100/toplamkota))  %>% group_by(university_name) %>%  arrange(desc(toplamkota))
print(head(dpr,100))
```
Fill rate of MEF University is as follows:
```{r}
dpr %>%  filter(university_name=="MEF ÜNÝVERSÝTESÝ")

```


